Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-13 hpmoon-asoco.tex
Some suggestions

Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
meaning that the
MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
Different authors have 
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. In this aspect, the
co-evolution model is a dimension-distributed model where a 
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. One
example of the application of this technique was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs different recombination
alternatives from the parts returned by worker processes. A high
dimensional problem was used to compare these 
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although in both papers
significant speedups were attained, only a low number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

@@

In our previous work \citep{Garcia16hpmoon} \textcolor{blue}{this method was used} in a
preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
\textcolor{blue}{It was shown}
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, \textcolor{blue}{the results showed} that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}. Besides comparing previous methods in this new experimental setup, in this paper 
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands \textcolor{blue}{is proposed}, comparing it with previous versions.

>>>>

Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
meaning that the
MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
% If this is the only justification, it should have been assessed at the end. It would be better if it was qualified, in the sense that more exploration is needed or something like that - JJ
Different authors have 
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. % Why should it improve quality? - JJ
In this aspect, the
co-evolution model is a dimension-distributed model where a 
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. One
example of the application of this technique was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs different recombination
alternatives from the parts returned by worker processes. A high
dimensional problem was used to compare these 
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although in both papers
significant speedups were attained, only a \textcolor{blue}{small} number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

@@

In our previous work \citep{Garcia16hpmoon} \textcolor{blue}{this method was used} in a
preliminary experimental setup, although it is worth mentioning \textcolor{blue}{that its name and acronym is established} in this paper for the first time.
\textcolor{blue}{It was shown}
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, \textcolor{blue}{the results showed} that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivate\textcolor{blue}{d} us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}. %Again, "testing more stuff" is not a good motivation. You should try to address a specific research question that might have been raised in the previous paper - JJ
Besides comparing previous methods in this new experimental setup, in this paper 
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands \textcolor{blue}{is proposed}, comparing it with previous versions.
